Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Remove redundant comma
Wording

We agree that type signatures are good abstract documentation~\cite{free}, but
there are many functions whose behavior cannot be guessed from their names and
type signatures.  One example is \verb|nub :: [a] -> [a]| from {\tt Data.List}.

@@

Evidence that is useful as user documentation, should be included in
Haddock comments.  For this purpose, we propose the following:

>>>>

We agree that a function's type can reveal something about a
function's behavior~\cite{free}, but
there are many functions whose behavior cannot be guessed from their names and
type signatures.  One example is \verb|nub :: [a] -> [a]| from {\tt Data.List}.

@@

Evidence that is useful as user documentation should be included in
Haddock comments.  For this purpose, we propose the following:
